---
title: "CaseStudy2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mosaic)
library(gapminder)
library(tidyverse)
library(ggplot2)
countrydata <- gapminder %>%
  filter(country != "Kuwait")


contavg <- countrydata %>%
  group_by(continent, year) %>%
  summarise(continentAvg = weighted.mean(gdpPercap,pop),
            population = mean(pop))
```

## R Markdown
Background:
There are a few main things that I learned from this project. One of the big things that I learned was how to add multiple lines from different datasets onto a single graph. This took me quite a while and I found it very difficult. I was able to find the answers to the things that I was looking for on websites like stackoverflow which I have bookmarked for future use.

I also learned how to create a weighted average using the function which I did not know how to do previously. Overall the thing that I am most proud of was how I was able to learn how to split up a dataset into multiple graphs like this, I think its a great way to represent this data. 

Images:


```{r}
ggplot(data = countrydata) +
  geom_point(mapping = aes(x = lifeExp, y = gdpPercap, color=continent, size = pop)) + 
  scale_y_continuous(trans = "sqrt")+
  facet_wrap(~ year, nrow = 1)
ggsave("gdplife.png", width=15)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot()+
  geom_point(data = countrydata, mapping = aes(x=year, y=gdpPercap, color=continent, group=country))+
  geom_line(data = countrydata, mapping = aes(x=year, y=gdpPercap, color=continent, group=country))+
  geom_point(data = contavg, mapping = aes(x=year, y=continentAvg, size=population))+
  geom_line(data = contavg, mapping = aes(x=year, y=continentAvg))+
  facet_wrap(~continent, nrow = 1)
ggsave("gdpyear.png", width=15)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
